Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Edit the figure 3

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.2, 1.9)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 6

>>>>

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.5, 1.47)
sc_ylims <- c(-0.32, 2.1)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 7
